\documentclass[12pt]{article}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{enumitem}
\begin{document}
\title{COSC221 Assignment 3}
\author{Rin Meng \\ Student ID: 51940633}
\maketitle


\begin{enumerate}[label=Part \Alph*)]
    \item
    \textbf{Remark:} 
	\begin{itemize}
    \item[-]
        $\mathbb{Z}^{+} = \{\forall n \in \mathbb{Z} : n \geq 1\} = \{1, 2, 3, \ldots\}$
    	\item[-]$\mathbb{Z}_{even}^{+} = \{n \in \mathbb{Z}^{+} : n \text{ mod } 2 = 0\} = \{2, 4, 6, \ldots\}$
    	\item[-]$\mathbb{Z}_{odd}^{+} = \mathbb{Z}^{+} \setminus \mathbb{Z}_{even}^{+} = \{1, 3, 5, \ldots\}$
	\end{itemize}

    \begin{proof}[Proof]
        By induction on $n \in \mathbb{Z}^{+}$. Here, we choose $\mathbb{Z}^{+}$ because it is more intuitive to have a positive integer of $n \times n$ chessboard. 
        
        Let $S(n) = n \times n$ chessboard, where there exists a rook's tour from top-left to bottom-left.
        
        \textbf{Base Case:} $n = 1$. It is known that a $1 \times 1$ chessboard is trivial, but ambiguous, so we can still proceed:
        
        $S(1) = 1 \times 1$ chessboard, so there exists one cell only on that chessboard, which makes it the top-left and the bottom-left cell at the same time, where the rook starts and ends at the same cell. Hence, there exists the rook's tour.
        
        \textbf{Inductive Hypothesis:} If our constructed $S(n)$ holds, then there exists some $n \in \mathbb{Z}^{+}$ such that it satisfies $S(n + 1)$ as well.
        
        \textbf{Inductive Step:} $n \rightarrow n + 1$.
        
$S(n+1) = (n + 1) \times (n + 1)$ chessboard. By the given information on page 234 for rook's tour and rook's move, we let $(x, y, k) \in \mathbb{Z}^{+}$, then it is true that rook can start at $\langle x, y \rangle$. Then from $n \times n$ chessboard to $(n + 1) \times (n + 1)$ chessboard, there are two possible movements:

		\begin{itemize}
    	\item[-] \textbf{Vertical movement:}
        $$\langle x, y \pm k \rangle \rightarrow \langle x, n+1 \rangle \Rightarrow y \pm k = n + 1 \Leftrightarrow y = n + 1 \pm k$$
    	\item[-] \textbf{Horizontal movement:}
        $$\langle x \pm k, y \rangle \rightarrow \langle n+1, y \rangle \Rightarrow x \pm k = n + 1 \Leftrightarrow x = n + 1 \pm k$$
		\end{itemize}

		Now, we know that, if we let
		$$k = min(\mathbb{Z}^{+}) = 1$$
		and, 
		$$min(x) = min(y) = n + 1 - k$$
		therefore,
		$$min(x) = min(y) = n + 1 - 1 = n$$
		Then, our movement for both vertical and horizontal are both within the bounds of $\mathbb{Z}^{+}$, as we said above, $k \in \mathbb{Z}^{+}$. Now, let these coordinates be true that $\langle 1, 1 \rangle \Rightarrow $ top-left, $\langle n + 1, 1 \rangle \Rightarrow $ top-right, $\langle 1, n + 1 \rangle \Rightarrow $ bottom-left and, $\langle n + 1, n + 1 \rangle \Rightarrow $ bottom-right. 

         Now to traverse through the board, there are two possible cases:
        
        \textbf{Case $\boldsymbol{\alpha}$:} $(n + 1) \times (n + 1)$ chessboard where $(n + 1) \in \mathbb{Z}_{\text{even}}^{+}$
        
        Then we let the rook start at $(1, 1)$,  we follow a horizontal ``zig-zag" pattern below:
        
        
        \begin{minipage}{\linewidth}
        \begin{center}
        $(1, 1) \rightarrow (2, 1) \rightarrow \ldots \rightarrow (n, 1) \rightarrow \underbrace{(n + 1, 1)}_{\downarrow}$
        
		$\underbrace{(1, 2)}_{\downarrow} \leftarrow (2, 2) \leftarrow \ldots \leftarrow  (n, 2) \leftarrow (n + 1, 2)$
		
		$(1, 3) \rightarrow (2, 3) \rightarrow \ldots \rightarrow  (n, 3) \rightarrow \underbrace{(n + 1, 3)}_{\downarrow}$
		
		$\hspace{168pt}\vdots\hspace{0pt}$
		
		$(1, n + 1) \leftarrow (2, n + 1) \leftarrow \ldots \leftarrow (n + 1, n + 1)$
		\end{center}
		\end{minipage}
		
		
		With this visual, we can clearly see that the rook arrives at the left side every time $y \in \mathbb{Z}_{\text{even}}^{+}$, so it is entirely possible that the rook can end up on the bottom-left side, because $max(y) = (n + 1) \in \mathbb{Z}_{\text{even}}^{+}$.
 
        \textbf{Case $\boldsymbol{\beta}$:} $(n + 1) \times (n + 1)$ chessboard where $(n + 1) \in \mathbb{Z}_{\text{odd}}^{+}$
        
        Then we let the rook start at $(1, 1)$,  we follow a vertical ``zig-zag" pattern below:
        
        
        \begin{minipage}{\linewidth}
        \begin{center}
        $\underbrace{(1, 1)}_{\downarrow} \quad\;\; (2, 1) \rightarrow \underbrace{(\ldots)}_{\downarrow} \quad\;\; (n, 1) \rightarrow \underbrace{(n + 1, 1)}_{\downarrow}$
        
		$\underbrace{\vdots}_{\downarrow} \quad\quad \overbrace{\vdots}^{\uparrow} \quad\;\; \underbrace{\vdots}_{\downarrow} \quad\;\;  \overbrace{(n, \vdots )}^{\uparrow} \quad\;\; \underbrace{(n + 1, 2)}_{\downarrow}$
		
		$(1, n) \rightarrow \overbrace{(2, n)}^{\uparrow} \quad\; (\ldots) \rightarrow \overbrace{(n, n)}^{\uparrow} \quad\;\; \underbrace{(n + 1, 3)}_{\downarrow}$
		
		$\hspace{178pt}\vdots\hspace{0pt}$
		
		$(1, n + 1) \leftarrow (2, n + 1) \leftarrow \ldots \leftarrow (n + 1, n + 1)$
		\end{center}
		\end{minipage}
		
		
		With this visual, we can clearly see that whenever $x \in \mathbb{Z}_{\text{odd}}^{+}$, it will be making a downwards movement, so since $max(x) = (n + 1) \in \mathbb{Z}_{\text{odd}}^{+}$, then we know that $x = n \in \mathbb{Z}_{\text{even}}^{+}$, that means that it will be making an upwards movement so that it can turn right towards $(n + 1, 1)$ where it can move down towards $(n+1, n)$. Note that we have never really visited $y = n + 1$ for these traversal, so let it be known that, after reaching $(n + 1, n + 1)$, it can go directly to $(1, n+1)$, where the rook will be at the bottom-left of the chessboard.
        
        $\therefore$ By mathematical induction, and by \textbf{Case} $\boldsymbol{\alpha}$ and $\boldsymbol{\beta}$, it is true that the rook's tour exists for the $n \times n$ chessboard, for some $n \in \mathbb{Z}^{+}$.
    \end{proof}
    
    \item \textbf{Remark:} We know that in a simple graph,
	$$directed \Rightarrow density = \frac{|E|}{\frac{n(n-1)}{2}} = \frac{2|E|}{n(n-1)}$$
	$$undirected \Rightarrow density =  \frac{|E|}{n(n-1)}$$
	Where $n$ is the vertex or node, and $|E|$ is the edges.
    
    \textbf{11.36} As a function of n the density of an n-node path means, $|E| \Rightarrow (n - 1)$, where $n$ is vertices, so we have,
	$$f(n) = \frac{2(n-1)}{n(n-1)} = \frac{2}{n}$$
	\textbf{11.37} As a function of n the density of an n-node cycle means, $|E| \Rightarrow n$, where $n$ is vertices, so we have,
	
	$$f(n) = \frac{2n}{n(n-1)} = \frac{2}{n - 1}$$
	
	\textbf{11.38} As a function of n the density of a graph that consists of $\frac{n}{3}$ disconnected triangles, $|E| \Rightarrow n$, where $n$ is vertices, so we have,
	
	$$f(n) = \frac{2n}{n(n-1)} = \frac{2}{n - 1}$$
	
	which is essentially the same as a cycle.
		
	\item \textbf{Remark:} Let it be known that clique 1, clique 2 and clique 3 represents the ``clusters" of nodes from left to right respectively in \textbf{Figure 11.33d}
	
	\textbf{11.54} We can see that each ``clusters" or cliques represents its own movie, then there must be at least, 3 movies, but it is also shown that there is 2 curves on the top of the graph, where the actor from the clique 3, knows actor from clique 1 and clique 2. which means that there must exists at least another 2 movies. Therefore, there must exists, at the minimum, five movies that could be generated by this collaboration network.
	
	
	
	\textbf{11.55} No, it is uncertain. It is entirely possible that there are more than 5 movies generated in this graph because each cliques can have its own subset, where the actors are in another movie different than the minimum 5 movies.
    
    \item 
    \textbf{11.95}
    \begin{proof}
    By counterexample, assume $G$ is a bipartite graph where,
    $$G = \langle L \cup R, E \rangle$$
    and where, $|L| = |R|$, so we can take, $L = \{1, 2\}$ and $R = \{3, 4\}$ and since all nodes from $L$ and $R$ has at least one neighbours, we can construct $G$ such that $E = \{\{1,3\}, \{2,4\}\}$, visually:
    
    
	\begin{center}
	\begin{tikzpicture}[scale=1.5]
    \tikzset{vertex/.style = {shape=circle,draw,minimum size=1.5em}}
    % Vertices in the left set L
    \foreach \pos/\name in {{(0,1)/1}, {(0,0)/2}}
        \node[vertex] (L\name) at \pos {$\name$};
    % Vertices in the right set R
    \foreach \pos/\name in {{(2,1)/3}, {(2,0)/4}}
        \node[vertex] (R\name) at \pos {$\name$};
    % Edges between vertices
    \foreach \source/\target in {L1/R3, L2/R4}
        \draw (\source) -- (\target);
	\end{tikzpicture}
	\end{center}
	
	We can see that the graph we made, $G$, consists of two disjoint sets which is absurd, because the original statement say that it is connected.
	
	$\therefore$ It is disproved that if $G = \langle L \cup R, E \rangle$ where $G$ is a bipartite graph with $|L| = |R|$, then it is impossible for $G$ to be a connected graph, if there is at minimum, one neighbour for every node in $L$ and $R$.
    \end{proof}
\end{enumerate}


End of Assignment 3.

\end{document}
